---
title: "basement_function"
format: html
---
```{r}
rm(list = ls())

# load all Packages ---
library(hdf5r)
library(sp)
library(sf)
library(ggplot2)
library(dplyr)
library(readr)
library(Metrics)
library(raster)
library(rgeos)
library(hydroGOF)
library(jsonlite)
```

# function
```{r}
basement <- function(model_json, mesh_path, simulation_json, setup_h5, results_h5, results_xdmf, results_json, discharge, strickler, time_end){

model <- fromJSON(model_json) #read in model json # modify it change mesh
model$SETUP$DOMAIN$BASEPLANE_2D$GEOMETRY$mesh_file <- mesh_path
model$SETUP$DOMAIN$BASEPLANE_2D$HYDRAULICS$BOUNDARY$STANDARD$discharge[1] <- discharge  #change discharge
model$SETUP$DOMAIN$BASEPLANE_2D$HYDRAULICS$FRICTION$default_friction <-  strickler #change Strickler

model_exp <- toJSON(model, pretty = TRUE, auto_unbox = TRUE) #export 
write(model_exp, "hdm_basement/model_new.json")

simulation <- fromJSON(simulation_json) #read in simulation json
simulation$SIMULATION$TIME$end <- time_end #modify it
simulation_exp <- toJSON(simulation, pretty = TRUE, auto_unbox = TRUE)
write(simulation_exp, "hdm_basement/simulation_new.json") #export 

# Set up BASEMENT
setup_cmd_name <- "c:\\Programme\\BASEMENT 3.2.0\\bin\\BMv3_BASEplane_setup.exe"
  setup_param1 = paste("-f ", getwd(), "\\", model_json, sep="")
  setup_param2 = paste("-o ", getwd(), "\\", setup_h5, sep="")
  system2(setup_cmd_name, args = c(setup_param1, setup_param2))

# Simulation in BASEMENT
simulation_cmd_name <- "c:\\Programme\\BASEMENT 3.2.0\\bin\\BMv3_BASEplane_omp.exe"
  simulation_param1 = paste("-f ", getwd(), "\\", simulation_json, sep="")
  simulation_param2 = paste("-r ", getwd(), "\\", setup_h5, sep="")
  simulation_param3 = paste("-o ", getwd(), "\\", results_h5,  sep="")
  system2(simulation_cmd_name, args = c(simulation_param1, simulation_param2,
                                        simulation_param3, "-p", "-n 16"))

  # Results of BASEMENT
results_cmd_name <- "c:\\Programme\\BASEMENT 3.2.0\\bin\\BMv3_BASEplane_results.exe"
  results_param1 = paste("-f ", getwd(), "\\", results_json, sep="")
  results_param2 = paste("-r ", getwd(), "\\", results_h5, sep="")
  results_param3 = paste("-o ", getwd(), "\\", results_xdmf, sep="")
  system2(results_cmd_name, args = c(results_param1, results_param2, results_param3))
}
```

# Test-Application of function 
```{r}
basement(model_json = "hdm_basement/model.json", 
         mesh_path = "hdm_basement/L2_mesh.2dm", 
         simulation_json = "hdm_basement/simulation.json",
         setup_h5 = "hdm_basement/setup.h5",
         results_h5 = "hdm_basement/results.h5",
         results_xdmf = "hdm_basement/results", #this can actually remain always the same
         results_json = "hdm_basement/results.json",
         discharge = 13, 
         strickler = 7, 
         time_end = 3600)

```

ERROR MESSAGE: 

BASEMENT v3.2.0
BASEplane setup binary
v3.2.0
Copyright: (C) 2022 ETH Zurich / Laboratory of hydraulics, hydrology and glaciology (VAW)

/SETUP/DOMAIN/BASEPLANE_2D/HYDRAULICS/BOUNDARY/STANDARD/0/slope: Warning: The value of this item will not be used.
 -> no model definition found
 -> ... unfortunately BASEMENT is killed!
BASEMENT v3.2.0
BASEplane cuda-sequential binary
v3.2.0
Copyright: (C) 2022 ETH Zurich / Laboratory of hydraulics, hydrology and glaciology (VAW)

 -> no model definition found
 -> ... unfortunately BASEMENT is killed!
BASEMENT v3.2.0
BASEplane results binary
v3.2.0
Copyright: (C) 2022 ETH Zurich / Laboratory of hydraulics, hydrology and glaciology (VAW)

 -> no model definition found
 -> ... unfortunately BASEMENT is killed!
