---
title: "Clean_Data"
format: html
---
# Clean Environment
```{r}
#clear R environment -------------------------------------------
rm(list = ls())
```


# Libraries 
```{r}

# Load the required packages
library("dplyr")
library("readr")
library("tidyr")
library("tidyverse")
library("stringr")
```

# Load Data
```{r}
# abiotic data
abiotic <- read_delim("Data/Abiotic_2022_2023_FINAL.csv")

# MI data field 
field <- read_delim("Data/MZB_Feldscreening.csv", col_names = FALSE)

# coordinate data from every location 
# Glenner 
gl1 <- read_delim("Data/GPS_Punkte/GL1.csv", col_names = FALSE)
gl2 <- read_delim("Data/GPS_Punkte/GL2.csv", col_names = FALSE)
gl3 <- read_delim("Data/GPS_Punkte/GL3.csv", col_names = FALSE)
gl4 <- read_delim("Data/GPS_Punkte/GL4.csv", col_names = FALSE)
gl5 <- read_delim("Data/GPS_Punkte/GL5.csv", col_names = FALSE)

# Landquart
l1 <- read_delim("Data/GPS_Punkte/L1.csv", col_names = FALSE)
l2 <- read_delim("Data/GPS_Punkte/L2.csv", col_names = FALSE)
l3 <- read_delim("Data/GPS_Punkte/L3.csv", col_names = FALSE)
l4 <- read_delim("Data/GPS_Punkte/L4.csv", col_names = FALSE)
lr <- read_delim("Data/GPS_Punkte/LR.csv", col_names = FALSE)

# Moesa 
m1 <- read_delim("Data/GPS_Punkte/M1.csv", col_names = FALSE)
m2 <- read_delim("Data/GPS_Punkte/M2.csv", col_names = FALSE)
m3 <- read_delim("Data/GPS_Punkte/M3.csv", col_names = FALSE)
m4 <- read_delim("Data/GPS_Punkte/M4.csv", col_names = FALSE)
m5 <- read_delim("Data/GPS_Punkte/M5.csv", col_names = FALSE)
m6 <- read_delim("Data/GPS_Punkte/M6.csv", col_names = FALSE)
m7 <- read_delim("Data/GPS_Punkte/M7.csv", col_names = FALSE)
mr <- read_delim("Data/GPS_Punkte/MR.csv", col_names = FALSE)

# Plessur
p1 <- read_delim("Data/GPS_Punkte/P1.csv", col_names = FALSE)
p2 <- read_delim("Data/GPS_Punkte/P2.csv", col_names = FALSE)
p3 <- read_delim("Data/GPS_Punkte/P3.csv", col_names = FALSE)
pr <- read_delim("Data/GPS_Punkte/PR.csv", col_names = FALSE)

# Sitter
s1 <- read_delim("Data/GPS_Punkte/S1.csv", col_names = FALSE)
s2 <- read_delim("Data/GPS_Punkte/S2.csv", col_names = FALSE)
s3 <- read_delim("Data/GPS_Punkte/S3.csv", col_names = FALSE)
s4 <- read_delim("Data/GPS_Punkte/S4.csv", col_names = FALSE)
s5 <- read_delim("Data/GPS_Punkte/S5.csv", col_names = FALSE)
s6 <- read_delim("Data/GPS_Punkte/S6.csv", col_names = FALSE)

# Saane 
sa1 <- read_delim("Data/GPS_Punkte/SA1.csv", col_names = FALSE)
sa2 <- read_delim("Data/GPS_Punkte/SA2.csv", col_names = FALSE)
sa3 <- read_delim("Data/GPS_Punkte/SA3.csv", col_names = FALSE)
sa4 <- read_delim("Data/GPS_Punkte/SA4.csv", col_names = FALSE)
sa5 <- read_delim("Data/GPS_Punkte/SA5.csv", col_names = FALSE)
sa6 <- read_delim("Data/GPS_Punkte/SA6.csv", col_names = FALSE)
sa7 <- read_delim("Data/GPS_Punkte/SA7.csv", col_names = FALSE)
sar <- read_delim("Data/GPS_Punkte/SAR.csv", col_names = FALSE)

# Sense/Singine 
se1 <- read_delim("Data/GPS_Punkte/SE1.csv", col_names = FALSE)
se2 <- read_delim("Data/GPS_Punkte/SE2-new.csv", col_names = FALSE)
se3 <- read_delim("Data/GPS_Punkte/SE3-NEW.csv", col_names = FALSE)
se4 <- read_delim("Data/GPS_Punkte/SE4.csv", col_names = FALSE)
sr <- read_delim("Data/GPS_Punkte/SR.csv", col_names = FALSE)

# Ticino 
t1 <- read_delim("Data/GPS_Punkte/T1.csv", col_names = FALSE)
t2 <- read_delim("Data/GPS_Punkte/T2.csv", col_names = FALSE)
t3 <- read_delim("Data/GPS_Punkte/T3.csv", col_names = FALSE)

# Thur 
th1 <- read_delim("Data/GPS_Punkte/th1.csv", col_names = FALSE)
th2 <- read_delim("Data/GPS_Punkte/th2.csv", col_names = FALSE)
th3 <- read_delim("Data/GPS_Punkte/TH3-NEW.csv", col_names = FALSE)
th4 <- read_delim("Data/GPS_Punkte/TH4-NEW.csv", col_names = FALSE)
th5 <- read_delim("Data/GPS_Punkte/th5.csv", col_names = FALSE)

# Verzasca
ve2 <- read_delim("Data/GPS_Punkte/VE2.csv", col_names = FALSE)
ve3 <- read_delim("Data/GPS_Punkte/VE3.csv", col_names = FALSE)
ve4 <- read_delim("Data/GPS_Punkte/VE4b.csv", col_names = FALSE)

# Vorderrhein 
vr1 <- read_delim("Data/GPS_Punkte/VR1.csv", col_names = FALSE)
vr2 <- read_delim("Data/GPS_Punkte/VR2.csv", col_names = FALSE)
vr3 <- read_delim("Data/GPS_Punkte/VR3.csv", col_names = FALSE)
vr4 <- read_delim("Data/GPS_Punkte/VR4.csv", col_names = FALSE)
vr5 <- read_delim("Data/GPS_Punkte/VR5.csv", col_names = FALSE)
vr6 <- read_delim("Data/GPS_Punkte/VR6.csv", col_names = FALSE)
```

# Create Join Key
## Abiotic Data
```{r}
# cut abiotic data into two datasets to join them together with the join_key
abiotic1 <- abiotic[ ,c(1:23)]
abiotic2 <- abiotic[ ,c(25:39)]

# abiotic data: create join key with "river-transect-sampling_point"
abiotic1 <- abiotic1 |>
  mutate(join_key = paste(`Reach (Untersuchungsstelle)...4`, Transect, `Sampling point`, sep = "-")) |>
  rename(Reach_Untersuchungsstelle = `Reach (Untersuchungsstelle)...4`)

abiotic2 <- abiotic2 |>
  rename(Reach_Untersuchungsstelle = `Reach (Untersuchungsstelle)...26`) |>
  

# join abiotic1 and abiotic2 together
abiotic_join <- full_join(abiotic1, abiotic2, by = "Reach_Untersuchungsstelle")
```

## MI Data
### Field Data
```{r}
# combine the first two rows together because we have two rows of headers
combined_row <- paste(field[1, ], field[2, ])

# remove the first two rows 
field <- field[-c(1:2), ]

# bind the combined rows to the field data
field <- rbind(combined_row, field)

# remove NA from first row 
row_index <- 1

# Remove single letters from the specified row
field[row_index, ] <- lapply(field[row_index, ], function(x) gsub("NA", " ", x))


# Assign the first row as the column names
colnames(field) <- field[1, ]

# remove first row 
field <- field[-1, ]

# field MI data: create join key with "river-transect-sampling_point"
field$join_key <- paste(field$` Sampling_site`, field$` Transect`, field$` Flow_range_location`, sep = "-")
```

### Lab Data
```{r}
# load MI data lab 
lab <- read_delim("Data/MZB_SBI_Labor.csv", col_names = FALSE)

# remove first two rows & third column
lab <- lab[-c(1:2), -3]

# Fill missing values and combine two rows  
lab <- lab |>
  fill(X1) |>
  mutate(X1 = paste(X1, X2, sep = " "))

# transpose dataframe 
t_lab <- as.data.frame(t(lab))


# Remove single letters from the specified row
row_index <- 1
t_lab[row_index, ] <- lapply(t_lab[row_index, ], function(x) gsub("NA", " ", x))

# make first row as header 
colnames(t_lab) <- t_lab[1, ]

# remove first and second row 
t_lab <- t_lab[-c(1:2), ]

# write .csv file 
write.csv(t_lab, "Data/MZB_Labor_intermediate.csv")

t_lab <- read_delim("Data/MZB_Labor_intermediate.csv")

# Fill missing values and combine two rows  
t_lab <- t_lab |>
  fill(`  Sampling_site`) |>
  select(-...1) |>
  function(x) gsub(`  Transekt - Kick`, "T", "", x)
```

## Coordinate Data 
```{r}
# coordinates: create the same join key "river-transect-sampling_point"
# function for column without characters in first column
join_key <- function(data, section){
data |>
  mutate(river = section,
         transect = head(rep(1:nrow(data), each = 3), nrow(data)),
         sampling_point = rep(c(3, 2, 1), length.out = nrow(data)),
         join_key = paste(river, transect, sampling_point, sep = "-")) 
}


# create join key for coordinates
# Glenner 
gl1 <- join_key(gl1, "GL1")
gl2 <- join_key(gl2, "GL2")
gl3 <- join_key(gl3, "GL3")
gl4 <- join_key(gl4, "GL4")
gl5 <- join_key(gl5, "GL5")

# Landquart
l1 <- join_key(l1, "L1")
l2 <- join_key(l2, "L2")
l3 <- join_key(l3, "L3")
l4 <- join_key(l4, "L4")
lr <- join_key(lr, "LR")

# Moesa 
m1 <- join_key(m1, "M1")
m2 <- join_key(m2, "M2")
m3 <- join_key(m3, "M3")
m4 <- join_key(m4, "M4")
m5 <- join_key(m5, "M5")
m6 <- join_key(m6, "M6")
m7 <- join_key(m7, "M7")
mr <- join_key(mr, "MR")

# Plessur 
p1 <- join_key(p1, "P1")
p2 <- join_key(p2, "P2")
p3 <- join_key(p3, "P3")
pr <- join_key(pr, "PR")

# Sitter
s1 <- join_key(s1, "S1")
s2 <- join_key(s2, "S2")
s3 <- join_key(s3, "S3")
s4 <- join_key(s4, "S4")
s5 <- join_key(s5, "S5")
s6 <- join_key(s6, "S6")

# Saane 
sa1 <- join_key(sa1, "SA1")
sa2 <- join_key(sa2, "SA2")
sa3 <- join_key(sa3, "SA3")
sa4 <- join_key(sa4, "SA4")
sa5 <- join_key(sa5, "SA5")
sa6 <- join_key(sa6, "SA6")
sa7 <- join_key(sa7, "SA7")
sar <- join_key(sar, "SAR")

# Sense/Singine 
se1 <- join_key(se1, "SE1")
se2 <- join_key(se2, "SE2")
se3 <- join_key(se3, "SE3")
se4 <- join_key(se4, "SE4")
sr <- join_key(sr, "SR")

# Ticino 
t1 <- join_key(t1, "T1")
t2 <- join_key(t2, "T2")
t3 <- join_key(t3, "T3")

# Thur 
th1 <- join_key(th1, "TH1")
th2 <- join_key(th2, "TH2")
th3 <- join_key(th3, "TH3")
th4 <- join_key(th4, "TH4")
th5 <- join_key(th5, "TH5")

# Verzasca
ve2 <- join_key(ve2, "VE2")
ve3 <- join_key(ve3, "VE3")
ve4 <- join_key(ve4, "VE4")

# Vorderrhein
vr1 <- join_key(vr1, "VR1")
vr2 <- join_key(vr2, "VR2")
vr3 <- join_key(vr3, "VR3")
vr4 <- join_key(vr4, "VR4") 
vr5 <- join_key(vr5, "VR5")
vr6 <- join_key(vr6, "VR6")
```

# Bind Coordinate DFs together
```{r}
# bind all coordinate dfs together  
coordinates <- rbind(gl1, gl2, gl3, gl4, gl5, l1, l2, l3, l4, lr, m1, m2, m3, m4, m5, m6, m7, mr, p1, p2, p3, pr, s1, s2, s3, s4, s5, s6, sa1, sa2, sa3, sa4, sa5, sa6, sa7, sar, se1, se2, se3, se4, sr, t1, t2, t3, th1, th2, th3, th4, th5, ve2, ve3, ve4, vr1, vr2, vr3, vr4, vr5, vr6)

# discard columns which are not needed & rename columns 
coordinates <- coordinates |>
  select(-X1, -X2, -river, -transect, -sampling_point) |>
  rename(x = X3, y = X4, z = X5)
```

# Join Dataframes 
```{r}
# anordnung noch ändern und column names geben 
# X3 = x, X4 = y, X5 = z
abiotic_full <- abiotic_join |>
  full_join(coordinates, by = "join_key") |>
  subset(join_key != "NA-NA-NA")

write.csv(abiotic_full, "Data/abiotic_full.csv")
```

  rename(River = c(River...1, River...25), Reach_Untersuchungsstelle = c(`Reach (Untersuchungsstelle)...4`, `Reach (Untersuchungsstelle)...26`), Abiotic_measured_by = c(`Abiotic measured by...5`, `Abiotic measured by...27`), Date_of_survey = c(`Date of survey...6`, `Date of survey...28`), Time_of_survey = c(`Time of survey...9`, `Time of survey...29`), pH = pH, Conductivity_μs_s = `Conductivity [μs/s]`, Oxygen_content_mg_l = `Oxygen content [mg/l]`, Oxygen_saturation_perc = `Oxygen saturation [%]`, Turbidity_FNU = `Turbidity [FNU]`, Temperature_C = `Temperature [°C]`, Discharge_m3_s = `Discharge [m3/s]`, Water_gauge_MueM = `Water gauge [MüM]`, Gauging_station = `Gauging station`, Varia = c(Varia...23, Varia...39), Sampling_point = `Sampling point`, Distance_Wasseranschlaglinie_m = `Distance "Wasseranschlaglinie" [m]`)