---
title: "Habitat_Model_VZH"
format: html
---

# Clear R environment 
```{r}
#clear R environment ---------------------------------------
rm(list = ls())
```

# Install and load packages 
```{r}
# check for a package, install and load ---------------------------------------
pkgCheck <- function(x){ 
  if (!require(x,character.only = TRUE)){
    install.packages(x,dependencies=TRUE)
    if(!require(x,character.only = TRUE)) {
      stop()
    }
  }
}

pkgCheck("raster")
pkgCheck("spsurvey")
pkgCheck("terra")
pkgCheck("raster")
pkgCheck("ggplot2")
pkgCheck("tibble")
pkgCheck("readr")
pkgCheck("dplyr")
pkgCheck("tidyr")
pkgCheck("scales")
```

# Load input rasters (velocity only)
```{r}
# Read raster-files of velocities ---------------------------------------
v_path <- "Data/raster_files"

# read raster-files ---------------------------------------
velocity_2 <- raster(file.path(v_path, "Landquart_results_velocity_2.tif"))
```

# FUNCTION 
## Reclassification
```{r}
# function for reclassified rasters without persistent habitats
# x = corresponding raster
reclass_raster <- function(x, output_file){
    x[x == 0] <- NA  # Set all 0-cells to NA
    reclass_table <- c(0, 0.05, 1, 
                   0.05, 0.25, 3, 
                   0.25, 0.75, 5,
                   0.75, 1.50, 4,
                   1.50, 2.50, 2,
                   2.50, Inf, NA) # Define reclassification table
    raster_classify <- reclassify(x, reclass_table,  include.lowest = TRUE)
    writeRaster(raster_classify, output_file, format = "GTiff", overwrite = TRUE)  # Save the reclassified raster
  return(raster_classify)
}

# Test <- reclass_raster(velocity_2, output_file = "Data/results_univariate/raster_classify_2.tif")
# plot(Test)

# function for reclassified rasters wit persistent habitats
# x = corresponding raster
# y = classified raster at base flow
reclass_raster_pers <- function(x, y, output_file){
  x[x == 0] <- NA  # Set all 0-cells to NA
    reclass_table <- c(0, 0.05, 1, 
                   0.05, 0.25, 3, 
                   0.25, 0.75, 5,
                   0.75, 1.50, 4,
                   1.50, 2.50, 2,
                   2.50, Inf, NA) # Define reclassification table
    raster_classify <- reclassify(x, reclass_table,  include.lowest = TRUE)
    pers_class <- mask(raster_classify, y)
    writeRaster(raster_classify, output_file, format = "GTiff", overwrite = TRUE)  # Save the reclassified raster
    return(raster_classify)
}

# Test_pers <- reclass_raster_pers(velocity_2, Test)
# plot(Test_pers)
```



# Habitat modelling 
# Read Suitability Curve 
```{r}
# Read suitability curve ---------------------------------------
HSC_path <- "Data/HSC_MI/HSC_MI.csv" 
HSC <- read.csv(HSC_path, sep=";", dec=".", header = TRUE)
```

# Univariate Habitat Model (Velocity Class)
```{r}
# Read raster-files of velocities ---------------------------------------
v_path <- "Data/results_univariate"

# read raster-files ---------------------------------------
v_2 <- raster(file.path(v_path, "raster_classify_2.tif"))
```

## FUNCTION HM 
```{r}
# define function for univariate calculation -----------------------------------
HM <- function(x, y = HSC$Bewohnbarkeitsklasse, z = HSC$HSI){
  univariat <- calc(x, fun = approxfun(y, z, rule = 2)) # Univariat habitat model
  wua <- cellStats(univariat, 'sum') * 4                       # WUA calculation 
  freq_table <- as.data.frame(freq(univariat, digit=1, useNA= "no"))  # freq_table calculation 
  sum(wua, freq_table)
  writeRaster(univariat, filename="Data/results_univariate/VZH_2.tif",
              format="GTiff", overwrite = TRUE)
  }

Test_HM <- HM(v_2)

plot(Test_HM)

# calculation for all Q's ---------------------------------------
VZH_2 <- univariat_v(v_2)


# Save the clipped raster-files ---------------------------------------
writeRaster(VZH_2, filename="QGIS_Project/results_univariate/VZH_2.tif", format="GTiff", overwrite = TRUE)
```

## Persistent Habitats of Habitat Model 
```{r}
# Clip the raster1 with raster2 ---------------------------------------
persistent_2 <- mask(VZH_2, VZH_2)


# Save the clipped raster-files ---------------------------------------
writeRaster(persistent_2, filename="QGIS_Project/results_univariate/persistent_VZH_2.tif", format="GTiff", overwrite = TRUE)
```

# Calculate WUA 
```{r}
# define function for WUA calculation -----------------------------------
wua <- function(x){
  cellStats(x, 'sum') * 4
}

# calculate WUA for all Q's -----------------------------------
WUA_VZH_2 <- wua(VZH_2)


# calculate WUA für pers. habitats for all Q's ----------------------------------
WUA_pers_2 <- wua(persistent_2)

```

# Calculate frequency table 
```{r}
# define function for feq_table calculation -----------------------------------
feq_table <- function(x){
  as.data.frame(freq(x, digit=1, useNA= "no"))
}

# calculate feq_table for all Q's -----------------------------------
freq_VZH_2 <- feq_table(VZH_2)
```

# Calculate WA_tot 
```{r}
# define function for WA_tot calculation -----------------------------------
wa_tot <- function(x, column_name){
  sum(x[[column_name]]) * 4
}

# calculate feq_table for all Q's -----------------------------------
WA_tot_VZH_2 <- wa_tot(freq_VZH_2, column_name = "count")
```

# Calculate HHS [-] 
```{r}
# calculate HHS for all Q's -----------------------------------
HHS_VZH_2 <- WUA_VZH_2/WA_tot_VZH_2

# calculate HHS persistent for all Q's -----------------------------------
HHS_pers_2 <- WUA_pers_2/WA_tot_VZH_2
```

# Create dataframe and .csv of calculated indices 
```{r}
# data frame WUA, HHS etc. -----------------------------------
results_VZH <- data.frame(Description = c("VZH", "VZH", "VZH", "VZH", "VZH", "VZH", "VZH", "VZH", "VZH", "VZH", "VZH", "VZH", "VZH"), Discharge = c(2.4, 3.9, 4.6, 7, 9, 11.4, 13.3, 15, 18.9, 22, 25, 28, 32.69), 
                      WUA_normal = c(WUA_VZH_2, WUA_VZH_3, WUA_VZH_4, WUA_VZH_7, WUA_VZH_9, WUA_VZH_11, WUA_VZH_13, WUA_VZH_15, WUA_VZH_18, WUA_VZH_22, WUA_VZH_25, WUA_VZH_28, WUA_VZH_32), 
                      WUA_pers = c(WUA_pers_2, WUA_pers_3, WUA_pers_4, WUA_pers_7, WUA_pers_9,  WUA_pers_11, WUA_pers_13, WUA_pers_15, WUA_pers_18, WUA_pers_22, WUA_pers_25, WUA_pers_28, WUA_pers_32),
                      HHS = c(HHS_VZH_2, HHS_VZH_3, HHS_VZH_4, HHS_VZH_7, HHS_VZH_9, HHS_VZH_11, HHS_VZH_13, HHS_VZH_15, HHS_VZH_18, HHS_VZH_22, HHS_VZH_25, HHS_VZH_28, HHS_VZH_32),
                      HHS_pers = c(HHS_pers_2, HHS_pers_3, HHS_pers_4, HHS_pers_7, HHS_pers_9, HHS_pers_11, HHS_pers_13, HHS_pers_15, HHS_pers_18, HHS_pers_22, HHS_pers_25, HHS_pers_28, HHS_pers_32),
                      WA_tot = c(WA_tot_VZH_2, WA_tot_VZH_3, WA_tot_VZH_4, WA_tot_VZH_7, WA_tot_VZH_9, WA_tot_VZH_11, WA_tot_VZH_13, WA_tot_VZH_15, WA_tot_VZH_18, WA_tot_VZH_22, WA_tot_VZH_25, WA_tot_VZH_28, WA_tot_VZH_32))

# safe df into .csv file -----------------------------------
write.csv(results_VZH, file = "results_statistics/Results_VZH_Habitat_Model.csv", row.names = FALSE)

# create dataframe for barchart visualisation 
freq_VZH_2 <- feq_table(raster_classify_2)
freq_VZH_9 <- feq_table(raster_classify_9)
freq_VZH_pers_9 <- feq_table(pers_class_9)


# bind together frequency table results for plots
join <- freq_VZH_2 |>
  full_join(freq_VZH_9, by = "value") |>
  full_join(freq_VZH_pers_9, by = "value")

# give colnames for plotting 
colnames(join) <- c("value", "VZH_2", "VZH_9", "VZH_pers_9")

# write data frame into .csv file
write.csv(join, file = "results_statistics/VZH.csv", row.names = FALSE)
```




