---
title: "Hydrodynamic_Model_Results"
format: html
---

# Load packages
```{r}
# clear R memory 
rm(list = ls())

# load packages 
pkgCheck <- function(x){ 
  if (!require(x,character.only = TRUE)){
    install.packages(x,dependencies=TRUE)
    if(!require(x,character.only = TRUE)) {
      stop()
    }
  }
}

pkgCheck("raster")
pkgCheck("spsurvey")
pkgCheck("terra")
pkgCheck("ggplot2")
pkgCheck("tibble")
pkgCheck("readr")
pkgCheck("dplyr")
pkgCheck("tidyr")
pkgCheck("scales")
pkgCheck("hdf5r")
pkgCheck("sp")
pkgCheck("sf")
pkgCheck("spatstat.geom")
pkgCheck("spatstat.explore")
pkgCheck("gstat")
pkgCheck("purrr")
pkgCheck("rgdal")

# load self-written functions 
source("mth_functions.R")
```

# plots - Glenner: GL1
## - Single Attribute Rasters
```{r}
 GL1_3_28 <- hdm_results(h5_path = "hdm_models/GL1/results_GL1_3_28.h5", 
                        twodm_path = "hdm_models/GL1/GL1_mesh_computational-mesh_3.2dm",
                        shp_path = "raster_files/GL1_shape.shp", 
                        raster_v_path = "raster_files/GL1_v_3_28.tif",
                        raster_wd_path = "raster_files/GL1_wd_3_28.tif")

 GL1_6_00 <- hdm_results(h5_path = "hdm_models/GL1/results_GL1_6_00.h5", 
                        twodm_path = "hdm_models/GL1/GL1_mesh_computational-mesh_3.2dm",
                        shp_path = "raster_files/GL1_shape.shp", 
                        raster_v_path = "raster_files/GL1_v_6_00.tif",
                        raster_wd_path = "raster_files/GL1_wd_6_00.tif")
 
GL1_9_00 <- hdm_results(h5_path = "hdm_models/GL1/results_GL1_9_00.h5", 
                        twodm_path = "hdm_models/GL1/GL1_mesh_computational-mesh_3.2dm",
                        shp_path = "raster_files/GL1_shape.shp", 
                        raster_v_path = "raster_files/GL1_v_9_00.tif",
                        raster_wd_path = "raster_files/GL1_wd_9_00.tif")
  
GL1_12_68 <- hdm_results(h5_path = "hdm_models/GL1/results_GL1_12_68.h5", 
                        twodm_path = "hdm_models/GL1/GL1_mesh_computational-mesh_3.2dm",
                        shp_path = "raster_files/GL1_shape.shp", 
                        raster_v_path = "raster_files/GL1_v_12_68.tif",
                        raster_wd_path = "raster_files/GL1_wd_12_68.tif")
   
GL1_16_00 <- hdm_results(h5_path = "hdm_models/GL1/results_GL1_16_00.h5", 
                        twodm_path = "hdm_models/GL1/GL1_mesh_computational-mesh_3.2dm",
                        shp_path = "raster_files/GL1_shape.shp", 
                        raster_v_path = "raster_files/GL1_v_16_00.tif",
                        raster_wd_path = "raster_files/GL1_wd_16_00.tif")

GL1_19_00 <- hdm_results(h5_path = "hdm_models/GL1/results_GL1_19_00.h5", 
                        twodm_path = "hdm_models/GL1/GL1_mesh_computational-mesh_3.2dm",
                        shp_path = "raster_files/GL1_shape.shp", 
                        raster_v_path = "raster_files/GL1_v_19_00.tif",
                        raster_wd_path = "raster_files/GL1_wd_19_00.tif")
 
GL1_22_00 <- hdm_results(h5_path = "hdm_models/GL1/results_GL1_22_00.h5", 
                        twodm_path = "hdm_models/GL1/GL1_mesh_computational-mesh_3.2dm",
                        shp_path = "raster_files/GL1_shape.shp", 
                        raster_v_path = "raster_files/GL1_v_22_00.tif",
                        raster_wd_path = "raster_files/GL1_wd_22_00.tif")

GL1_25_00 <- hdm_results(h5_path = "hdm_models/GL1/results_GL1_25_00.h5", 
                        twodm_path = "hdm_models/GL1/GL1_mesh_computational-mesh_3.2dm",
                        shp_path = "raster_files/GL1_shape.shp", 
                        raster_v_path = "raster_files/GL1_v_25_00.tif",
                        raster_wd_path = "raster_files/GL1_wd_25_00.tif")
 
GL1_28_00 <- hdm_results(h5_path = "hdm_models/GL1/results_GL1_28_00.h5", 
                        twodm_path = "hdm_models/GL1/GL1_mesh_computational-mesh_3.2dm",
                        shp_path = "raster_files/GL1_shape.shp", 
                        raster_v_path = "raster_files/GL1_v_28_00.tif",
                        raster_wd_path = "raster_files/GL1_wd_28_00.tif")

GL1_31_76 <- hdm_results(h5_path = "hdm_models/GL1/results_GL1_31_76.h5", 
                        twodm_path = "hdm_models/GL1/GL1_mesh_computational-mesh_3.2dm",
                        shp_path = "raster_files/GL1_shape.shp", 
                        raster_v_path = "raster_files/GL1_v_31_76.tif",
                        raster_wd_path = "raster_files/GL1_wd_31_76.tif")
```

## - Stacked Rasters 
```{r}
GL1_stacked_3_28 <- stack_raster(v_path = "raster_files/GL1_v_3_28.tif",
                                wd_path = "raster_files/GL1_wd_3_28.tif",
                                stack_path = "rasters_stacked/GL1_3_28.grd")

GL1_stacked_6_00 <- stack_raster(v_path = "raster_files/GL1_v_6_00.tif",
                                wd_path = "raster_files/GL1_wd_6_00.tif",
                                stack_path = "rasters_stacked/GL1_6_00.grd")

GL1_stacked_9_00 <- stack_raster(v_path = "raster_files/GL1_v_9_00.tif",
                                wd_path = "raster_files/GL1_wd_9_00.tif",
                                stack_path = "rasters_stacked/GL1_9_00.grd")

GL1_stacked_12_68 <- stack_raster(v_path = "raster_files/GL1_v_12_68.tif",
                                wd_path = "raster_files/GL1_wd_12_68.tif",
                                stack_path = "rasters_stacked/GL1_12_68.grd")

GL1_stacked_16_00 <- stack_raster(v_path = "raster_files/GL1_v_16_00.tif",
                                wd_path = "raster_files/GL1_wd_16_00.tif",
                                stack_path = "rasters_stacked/GL1_16_00.grd")

GL1_stacked_19_00 <- stack_raster(v_path = "raster_files/GL1_v_19_00.tif",
                                wd_path = "raster_files/GL1_wd_19_00.tif",
                                stack_path = "rasters_stacked/GL1_19_00.grd")

GL1_stacked_22_00 <- stack_raster(v_path = "raster_files/GL1_v_22_00.tif",
                                wd_path = "raster_files/GL1_wd_22_00.tif",
                                stack_path = "rasters_stacked/GL1_22_00.grd")

GL1_stacked_25_00 <- stack_raster(v_path = "raster_files/GL1_v_25_00.tif",
                                wd_path = "raster_files/GL1_wd_25_00.tif",
                                stack_path = "rasters_stacked/GL1_25_00.grd")

GL1_stacked_28_00 <- stack_raster(v_path = "raster_files/GL1_v_28_00.tif",
                                wd_path = "raster_files/GL1_wd_28_00.tif",
                                stack_path = "rasters_stacked/GL1_28_00.grd")

GL1_stacked_31_76 <- stack_raster(v_path = "raster_files/GL1_v_31_76.tif",
                                wd_path = "raster_files/GL1_wd_31_76.tif",
                                stack_path = "rasters_stacked/GL1_31_76.grd")
```

# plots - Glenner: GL2
## - Single Attribute Rasters
```{r}
GL2_3_21 <- hdm_results(h5_path = "hdm_models/GL2/results_GL2_3_21.h5", 
                        twodm_path = "hdm_models/GL2/Gl2_computational-mesh_mod.2dm",
                        shp_path = "raster_files/GL2_shape.shp", 
                        raster_v_path = "raster_files/GL2_v_3_21.tif",
                        raster_wd_path = "raster_files/GL2_wd_3_21.tif")

GL2_6_00 <- hdm_results(h5_path = "hdm_models/GL2/results_GL2_6_00.h5", 
                        twodm_path = "hdm_models/GL2/Gl2_computational-mesh_mod.2dm",
                        shp_path = "raster_files/GL2_shape.shp", 
                        raster_v_path = "raster_files/GL2_v_6_00.tif",
                        raster_wd_path = "raster_files/GL2_wd_6_00.tif")

GL2_9_00 <- hdm_results(h5_path = "hdm_models/GL2/results_GL2_9_00.h5", 
                        twodm_path = "hdm_models/GL2/Gl2_computational-mesh_mod.2dm",
                        shp_path = "raster_files/GL2_shape.shp", 
                        raster_v_path = "raster_files/GL2_v_9_00.tif",
                        raster_wd_path = "raster_files/GL2_wd_9_00.tif")

GL2_11_00 <- hdm_results(h5_path = "hdm_models/GL2/results_GL2_11_00.h5", 
                        twodm_path = "hdm_models/GL2/Gl2_computational-mesh_mod.2dm",
                        shp_path = "raster_files/GL2_shape.shp", 
                        raster_v_path = "raster_files/GL2_v_11_00.tif",
                        raster_wd_path = "raster_files/GL2_wd_11_00.tif")

GL2_12_52 <- hdm_results(h5_path = "hdm_models/GL2/results_GL2_12_52.h5", 
                        twodm_path = "hdm_models/GL2/Gl2_computational-mesh_mod.2dm",
                        shp_path = "raster_files/GL2_shape.shp", 
                        raster_v_path = "raster_files/GL2_v_12_52.tif",
                        raster_wd_path = "raster_files/GL2_wd_12_52.tif")

GL2_16_00 <- hdm_results(h5_path = "hdm_models/GL2/results_GL2_16_00.h5", 
                        twodm_path = "hdm_models/GL2/Gl2_computational-mesh_mod.2dm",
                        shp_path = "raster_files/GL2_shape.shp", 
                        raster_v_path = "raster_files/GL2_v_16_00.tif",
                        raster_wd_path = "raster_files/GL2_wd_16_00.tif")

GL2_19_00 <- hdm_results(h5_path = "hdm_models/GL2/results_GL2_19_00.h5", 
                        twodm_path = "hdm_models/GL2/Gl2_computational-mesh_mod.2dm",
                        shp_path = "raster_files/GL2_shape.shp", 
                        raster_v_path = "raster_files/GL2_v_19_00.tif",
                        raster_wd_path = "raster_files/GL2_wd_19_00.tif")

GL2_22_00 <- hdm_results(h5_path = "hdm_models/GL2/results_GL2_22_00.h5", 
                        twodm_path = "hdm_models/GL2/Gl2_computational-mesh_mod.2dm",
                        shp_path = "raster_files/GL2_shape.shp", 
                        raster_v_path = "raster_files/GL2_v_22_00.tif",
                        raster_wd_path = "raster_files/GL2_wd_22_00.tif")

GL2_25_00 <- hdm_results(h5_path = "hdm_models/GL2/results_GL2_25_00.h5", 
                        twodm_path = "hdm_models/GL2/Gl2_computational-mesh_mod.2dm",
                        shp_path = "raster_files/GL2_shape.shp", 
                        raster_v_path = "raster_files/GL2_v_25_00.tif",
                        raster_wd_path = "raster_files/GL2_wd_25_00.tif")

GL2_28_00 <- hdm_results(h5_path = "hdm_models/GL2/results_GL2_28_00.h5", 
                        twodm_path = "hdm_models/GL2/Gl2_computational-mesh_mod.2dm",
                        shp_path = "raster_files/GL2_shape.shp", 
                        raster_v_path = "raster_files/GL2_v_28_00.tif",
                        raster_wd_path = "raster_files/GL2_wd_28_00.tif")

GL2_31_53 <- hdm_results(h5_path = "hdm_models/GL2/results_GL2_31_53.h5", 
                        twodm_path = "hdm_models/GL2/Gl2_computational-mesh_mod.2dm",
                        shp_path = "raster_files/GL2_shape.shp", 
                        raster_v_path = "raster_files/GL2_v_31_53.tif",
                        raster_wd_path = "raster_files/GL2_wd_31_53.tif")

par(mfrow=c(4,4))
test_v <- raster("raster_files/GL2_v_31_53.tif")
test_wd <- raster("raster_files/GL2_wd_31_53.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

test_v <- raster("raster_files/GL2_v_28_00.tif")
test_wd <- raster("raster_files/GL2_wd_28_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

test_v <- raster("raster_files/GL2_v_25_00.tif")
test_wd <- raster("raster_files/GL2_wd_25_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

test_v <- raster("raster_files/GL2_v_22_00.tif")
test_wd <- raster("raster_files/GL2_wd_22_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

test_v <- raster("raster_files/GL2_v_19_00.tif")
test_wd <- raster("raster_files/GL2_wd_19_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

test_v <- raster("raster_files/GL2_v_16_00.tif")
test_wd <- raster("raster_files/GL2_wd_16_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

test_v <- raster("raster_files/GL2_v_12_52.tif")
test_wd <- raster("raster_files/GL2_wd_12_52.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

test_v <- raster("raster_files/GL2_v_11_00.tif")
test_wd <- raster("raster_files/GL2_wd_11_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

test_v <- raster("raster_files/GL2_v_9_00.tif")
test_wd <- raster("raster_files/GL2_wd_9_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

test_v <- raster("raster_files/GL2_v_6_00.tif")
test_wd <- raster("raster_files/GL2_wd_6_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

test_v <- raster("raster_files/GL2_v_3_21.tif")
test_wd <- raster("raster_files/GL2_wd_3_21.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)
```

## - Stacked Rasters 
```{r}
GL2_stacked_3_21 <- stack_raster(v_path = "raster_files/GL2_v_3_21.tif",
                                wd_path = "raster_files/GL2_wd_3_21.tif",
                                stack_path = "rasters_stacked/GL2_3_21.grd")

GL2_stacked_6_00 <- stack_raster(v_path = "raster_files/GL2_v_6_00.tif",
                                wd_path = "raster_files/GL2_wd_6_00.tif",
                                stack_path = "rasters_stacked/GL2_6_00.grd")

GL2_stacked_9_00 <- stack_raster(v_path = "raster_files/GL2_v_9_00.tif",
                                wd_path = "raster_files/GL2_wd_9_00.tif",
                                stack_path = "rasters_stacked/GL2_9_00.grd")

GL2_stacked_11_00 <- stack_raster(v_path = "raster_files/GL2_v_11_00.tif",
                                wd_path = "raster_files/GL2_wd_11_00.tif",
                                stack_path = "rasters_stacked/GL2_11_00.grd")

GL2_stacked_12_52 <- stack_raster(v_path = "raster_files/GL2_v_12_52.tif",
                                wd_path = "raster_files/GL2_wd_12_52.tif",
                                stack_path = "rasters_stacked/GL2_12_52.grd")

GL2_stacked_16_00 <- stack_raster(v_path = "raster_files/GL2_v_16_00.tif",
                                wd_path = "raster_files/GL2_wd_16_00.tif",
                                stack_path = "rasters_stacked/GL2_16_00.grd")

GL2_stacked_19_00 <- stack_raster(v_path = "raster_files/GL2_v_19_00.tif",
                                wd_path = "raster_files/GL2_wd_19_00.tif",
                                stack_path = "rasters_stacked/GL2_19_00.grd")

GL2_stacked_22_00 <- stack_raster(v_path = "raster_files/GL2_v_22_00.tif",
                                wd_path = "raster_files/GL2_wd_22_00.tif",
                                stack_path = "rasters_stacked/GL2_22_00.grd")

GL2_stacked_25_00 <- stack_raster(v_path = "raster_files/GL2_v_25_00.tif",
                                wd_path = "raster_files/GL2_wd_25_00.tif",
                                stack_path = "rasters_stacked/GL2_25_00.grd")

GL2_stacked_28_00 <- stack_raster(v_path = "raster_files/GL2_v_28_00.tif",
                                wd_path = "raster_files/GL2_wd_28_00.tif",
                                stack_path = "rasters_stacked/GL2_28_00.grd")

GL2_stacked_31_53 <- stack_raster(v_path = "raster_files/GL2_v_31_53.tif",
                                wd_path = "raster_files/GL2_wd_31_53.tif",
                                stack_path = "rasters_stacked/GL2_31_53.grd")
```

# - Landquart: L2
## - Single Attribute Rasters
```{r}
par(mfrow=c(4,4))

L2_2_40 <- hdm_results(h5_path = "hdm_models/L2/results_L2_2_40.h5", 
                       twodm_path = "hdm_models/L2/Landquart_computational-mesh_anto_depthcorr.2dm",
                       shp_path = "raster_files/L2_shape.shp", 
                       raster_v_path = "raster_files/L2_v_2_40.tif",
                       raster_wd_path = "raster_files/L2_wd_2_40.tif")

test_v <- raster("raster_files/L2_v_2_40.tif")
test_wd <- raster("raster_files/L2_wd_2_40.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

L2_3_90 <- hdm_results(h5_path = "hdm_models/L2/results_L2_3_90.h5", 
                       twodm_path = "hdm_models/L2/Landquart_computational-mesh_anto_depthcorr.2dm",
                       shp_path = "raster_files/L2_shape.shp", 
                       raster_v_path = "raster_files/L2_v_3_90.tif",
                       raster_wd_path = "raster_files/L2_wd_3_90.tif")

test_v <- raster("raster_files/L2_v_3_90.tif")
test_wd <- raster("raster_files/L2_wd_3_90.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

L2_7_00 <- hdm_results(h5_path = "hdm_models/L2/results_L2_7_00.h5", 
                       twodm_path = "hdm_models/L2/Landquart_computational-mesh_anto_depthcorr.2dm",
                       shp_path = "raster_files/L2_shape.shp", 
                       raster_v_path = "raster_files/L2_v_7_00.tif",
                       raster_wd_path = "raster_files/L2_wd_7_00.tif")

test_v <- raster("raster_files/L2_v_7_00.tif")
test_wd <- raster("raster_files/L2_wd_7_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

L2_9_24 <- hdm_results(h5_path = "hdm_models/L2/results_L2_9_24.h5", 
                       twodm_path = "hdm_models/L2/Landquart_computational-mesh_anto_depthcorr.2dm",
                       shp_path = "raster_files/L2_shape.shp", 
                       raster_v_path = "raster_files/L2_v_9_24.tif",
                       raster_wd_path = "raster_files/L2_wd_9_24.tif")

test_v <- raster("raster_files/L2_v_9_24.tif")
test_wd <- raster("raster_files/L2_wd_9_24.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

L2_11_40 <- hdm_results(h5_path = "hdm_models/L2/results_L2_11_40.h5", 
                       twodm_path = "hdm_models/L2/Landquart_computational-mesh_anto_depthcorr.2dm",
                       shp_path = "raster_files/L2_shape.shp", 
                       raster_v_path = "raster_files/L2_v_11_40.tif",
                       raster_wd_path = "raster_files/L2_wd_11_40.tif")

test_v <- raster("raster_files/L2_v_11_40.tif")
test_wd <- raster("raster_files/L2_wd_11_40.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

L2_13_30 <- hdm_results(h5_path = "hdm_models/L2/results_L2_13_30.h5", 
                       twodm_path = "hdm_models/L2/Landquart_computational-mesh_anto_depthcorr.2dm",
                       shp_path = "raster_files/L2_shape.shp", 
                       raster_v_path = "raster_files/L2_v_13_30.tif",
                       raster_wd_path = "raster_files/L2_wd_13_30.tif")

test_v <- raster("raster_files/L2_v_13_30.tif")
test_wd <- raster("raster_files/L2_wd_13_30.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

L2_16_50 <- hdm_results(h5_path = "hdm_models/L2/results_L2_16_50.h5", 
                       twodm_path = "hdm_models/L2/Landquart_computational-mesh_anto_depthcorr.2dm",
                       shp_path = "raster_files/L2_shape.shp", 
                       raster_v_path = "raster_files/L2_v_16_50.tif",
                       raster_wd_path = "raster_files/L2_wd_16_50.tif")

test_v <- raster("raster_files/L2_v_16_50.tif")
test_wd <- raster("raster_files/L2_wd_16_50.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

L2_18_90 <- hdm_results(h5_path = "hdm_models/L2/results_L2_18_90.h5", 
                       twodm_path = "hdm_models/L2/Landquart_computational-mesh_anto_depthcorr.2dm",
                       shp_path = "raster_files/L2_shape.shp", 
                       raster_v_path = "raster_files/L2_v_18_90.tif",
                       raster_wd_path = "raster_files/L2_wd_18_90.tif")

test_v <- raster("raster_files/L2_v_18_90.tif")
test_wd <- raster("raster_files/L2_wd_18_90.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)
```

## - Stacked Raster
```{r}
L2_stacked_2_40 <- stack_raster(v_path = "raster_files/L2_v_2_40.tif",
                                wd_path = "raster_files/L2_wd_2_40.tif",
                                stack_path = "rasters_stacked/L2_2_40.grd")

L2_stacked_3_90 <- stack_raster(v_path = "raster_files/L2_v_3_90.tif",
                                wd_path = "raster_files/L2_wd_3_90.tif",
                                stack_path = "rasters_stacked/L2_3_90.grd")

L2_stacked_7_00 <- stack_raster(v_path = "raster_files/L2_v_7_00.tif",
                                wd_path = "raster_files/L2_wd_7_00.tif",
                                stack_path = "rasters_stacked/L2_7_00.grd")

L2_stacked_9_24 <- stack_raster(v_path = "raster_files/L2_v_9_24.tif",
                                wd_path = "raster_files/L2_wd_9_24.tif",
                                stack_path = "rasters_stacked/L2_9_24.grd")

L2_stacked_11_40 <- stack_raster(v_path = "raster_files/L2_v_11_40.tif",
                                wd_path = "raster_files/L2_wd_11_40.tif",
                                stack_path = "rasters_stacked/L2_11_40.grd")

L2_stacked_13_30 <- stack_raster(v_path = "raster_files/L2_v_13_30.tif",
                                wd_path = "raster_files/L2_wd_13_30.tif",
                                stack_path = "rasters_stacked/L2_13_30.grd")

L2_stacked_16_50 <- stack_raster(v_path = "raster_files/L2_v_16_50.tif",
                                wd_path = "raster_files/L2_wd_16_50.tif",
                                stack_path = "rasters_stacked/L2_16_50.grd")

L2_stacked_18_90 <- stack_raster(v_path = "raster_files/L2_v_18_90.tif",
                                wd_path = "raster_files/L2_wd_18_90.tif",
                                stack_path = "rasters_stacked/L2_18_90.grd")
```

# plots - Moesa: M1
## M1_18_84 Single Attribute Rasters
```{r}
M1_0_47 <- hdm_results(h5_path = "hdm_models/M1/results_M1_0_47.h5", 
                       twodm_path = "hdm_models/M1/moesa_mzb_uebersicht_computational-mesh2.2dm",
                       shp_path = "raster_files/M1_shape.shp", 
                       raster_v_path = "raster_files/M1_v_0_47.tif",
                       raster_wd_path = "raster_files/M1_wd_0_47.tif")

test <- raster("raster_files/M1_v_0_47.tif")
crs(test) <- "EPSG: 2056"
plot(test)

M1_0_60 <- hdm_results(h5_path = "hdm_models/M1/results_M1_0_60.h5", 
                       twodm_path = "hdm_models/M1/moesa_mzb_uebersicht_computational-mesh2.2dm",
                       shp_path = "raster_files/M1_shape.shp", 
                       raster_v_path = "raster_files/M1_v_0_60.tif",
                       raster_wd_path = "raster_files/M1_wd_0_60.tif")

test <- raster("raster_files/M1_v_0_60.tif")
crs(test) <- "EPSG: 2056"
plot(test)

M1_4_00 <- hdm_results(h5_path = "hdm_models/M1/results_M1_4_00.h5", 
                       twodm_path = "hdm_models/M1/moesa_mzb_uebersicht_computational-mesh2.2dm",
                       shp_path = "raster_files/M1_shape.shp", 
                       raster_v_path = "raster_files/M1_v_4_00.tif",
                       raster_wd_path = "raster_files/M1_wd_4_00.tif")

test <- raster("raster_files/M1_v_4_00.tif")
crs(test) <- "EPSG: 2056"
plot(test)

M1_6_00 <- hdm_results(h5_path = "hdm_models/M1/results_M1_6_00.h5", 
                       twodm_path = "hdm_models/M1/moesa_mzb_uebersicht_computational-mesh2.2dm",
                       shp_path = "raster_files/M1_shape.shp", 
                       raster_v_path = "raster_files/M1_v_6_00.tif",
                       raster_wd_path = "raster_files/M1_wd_6_00.tif")

test <- raster("raster_files/M1_v_6_00.tif")
crs(test) <- "EPSG: 2056"
plot(test)

M1_8_00 <- hdm_results(h5_path = "hdm_models/M1/results_M1_8_00.h5", 
                       twodm_path = "hdm_models/M1/moesa_mzb_uebersicht_computational-mesh2.2dm",
                       shp_path = "raster_files/M1_shape.shp", 
                       raster_v_path = "raster_files/M1_v_8_00.tif",
                       raster_wd_path = "raster_files/M1_wd_8_00.tif")

test <- raster("raster_files/M1_v_8_00.tif")
crs(test) <- "EPSG: 2056"
plot(test)

M1_10_00 <- hdm_results(h5_path = "hdm_models/M1/results_M1_10_00.h5", 
                       twodm_path = "hdm_models/M1/moesa_mzb_uebersicht_computational-mesh2.2dm",
                       shp_path = "raster_files/M1_shape.shp", 
                       raster_v_path = "raster_files/M1_v_10_00.tif",
                       raster_wd_path = "raster_files/M1_wd_10_00.tif")

test <- raster("raster_files/M1_v_10_00.tif")
crs(test) <- "EPSG: 2056"
plot(test)

M1_12_00 <- hdm_results(h5_path = "hdm_models/M1/results_M1_12_00.h5", 
                       twodm_path = "hdm_models/M1/moesa_mzb_uebersicht_computational-mesh2.2dm",
                       shp_path = "raster_files/M1_shape.shp", 
                       raster_v_path = "raster_files/M1_v_12_00.tif",
                       raster_wd_path = "raster_files/M1_wd_12_00.tif")

test <- raster("raster_files/M1_v_12_00.tif")
crs(test) <- "EPSG: 2056"
plot(test)

M1_14_00 <- hdm_results(h5_path = "hdm_models/M1/results_M1_14_00.h5", 
                       twodm_path = "hdm_models/M1/moesa_mzb_uebersicht_computational-mesh2.2dm",
                       shp_path = "raster_files/M1_shape.shp", 
                       raster_v_path = "raster_files/M1_v_14_00.tif",
                       raster_wd_path = "raster_files/M1_wd_14_00.tif")

test <- raster("raster_files/M1_v_14_00.tif")
crs(test) <- "EPSG: 2056"
plot(test)

M1_16_00 <- hdm_results(h5_path = "hdm_models/M1/results_M1_16_00.h5", 
                       twodm_path = "hdm_models/M1/moesa_mzb_uebersicht_computational-mesh2.2dm",
                       shp_path = "raster_files/M1_shape.shp", 
                       raster_v_path = "raster_files/M1_v_16_00.tif",
                       raster_wd_path = "raster_files/M1_wd_16_00.tif")

par(mfrow=c(4,4))
test_v <- raster("raster_files/M1_v_16_00.tif")
test_wd <- raster("raster_files/M1_wd_16_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

M1_18_84 <- hdm_results(h5_path = "hdm_models/M1/results_M1_18_84.h5", 
                       twodm_path = "hdm_models/M1/moesa_mzb_uebersicht_computational-mesh2.2dm",
                       shp_path = "raster_files/M1_shape.shp", 
                       raster_v_path = "raster_files/M1_v_18_84.tif",
                       raster_wd_path = "raster_files/M1_wd_18_84.tif")

test_v <- raster("raster_files/M1_v_18_84.tif")
test_wd <- raster("raster_files/M1_wd_18_84.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

M1_22_84 <- hdm_results(h5_path = "hdm_models/M1/results_M1_22_84.h5", 
                       twodm_path = "hdm_models/M1/moesa_mzb_uebersicht_computational-mesh2.2dm",
                       shp_path = "raster_files/M1_shape.shp", 
                       raster_v_path = "raster_files/M1_v_22_84.tif",
                       raster_wd_path = "raster_files/M1_wd_22_84.tif")

test_v <- raster("raster_files/M1_v_22_84.tif")
test_wd <- raster("raster_files/M1_wd_22_84.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)
```

## Stacked Rasters
```{r}
M1_stacked_0_47 <- stack_raster(v_path = "raster_files/M1_v_0_47.tif",
                                wd_path = "raster_files/M1_wd_0_47.tif",
                                stack_path = "rasters_stacked/M1_0_47.grd")

M1_stacked_0_60 <- stack_raster(v_path = "raster_files/M1_v_0_60.tif",
                                wd_path = "raster_files/M1_wd_0_60.tif",
                                stack_path = "rasters_stacked/M1_0_60.grd")

M1_stacked_4_00 <- stack_raster(v_path = "raster_files/M1_v_4_00.tif",
                                wd_path = "raster_files/M1_wd_4_00.tif",
                                stack_path = "rasters_stacked/M1_4_00.grd")

M1_stacked_6_00 <- stack_raster(v_path = "raster_files/M1_v_6_00.tif",
                                wd_path = "raster_files/M1_wd_6_00.tif",
                                stack_path = "rasters_stacked/M1_6_00.grd")

M1_stacked_8_00 <- stack_raster(v_path = "raster_files/M1_v_8_00.tif",
                                wd_path = "raster_files/M1_wd_8_00.tif",
                                stack_path = "rasters_stacked/M1_8_00.grd")

M1_stacked_10_00 <- stack_raster(v_path = "raster_files/M1_v_10_00.tif",
                                wd_path = "raster_files/M1_wd_10_00.tif",
                                stack_path = "rasters_stacked/M1_10_00.grd")

M1_stacked_12_00 <- stack_raster(v_path = "raster_files/M1_v_12_00.tif",
                                wd_path = "raster_files/M1_wd_12_00.tif",
                                stack_path = "rasters_stacked/M1_12_00.grd")

M1_stacked_14_00 <- stack_raster(v_path = "raster_files/M1_v_14_00.tif",
                                wd_path = "raster_files/M1_wd_14_00.tif",
                                stack_path = "rasters_stacked/M1_14_00.grd")

M1_stacked_16_00 <- stack_raster(v_path = "raster_files/M1_v_16_00.tif",
                                wd_path = "raster_files/M1_wd_16_00.tif",
                                stack_path = "rasters_stacked/M1_16_00.grd")

M1_stacked_18_84 <- stack_raster(v_path = "raster_files/M1_v_18_84.tif",
                                wd_path = "raster_files/M1_wd_18_84.tif",
                                stack_path = "rasters_stacked/M1_18_84.grd")

M1_stacked_22_84 <- stack_raster(v_path = "raster_files/M1_v_22_84.tif",
                                wd_path = "raster_files/M1_wd_22_84.tif",
                                stack_path = "rasters_stacked/M1_22_84.grd")
```

# Sitter: S1
## Single Attribute Rasters
```{r}
par(mfrow=c(4,4))

S1_2_00 <- hdm_results(h5_path = "hdm_models/S1/results_S1_2_00.h5", 
                    twodm_path = "hdm_models/S1/S1_mesh_computational-mesh1.2dm",
                    shp_path = "raster_files/S1_shape.shp", 
                    raster_v_path = "raster_files/S1_v_2_00.tif",
                    raster_wd_path = "raster_files/S1_wd_2_00.tif")

test_v <- raster("raster_files/S1_v_2_00.tif")
test_wd <- raster("raster_files/S1_wd_2_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S1_3_70 <- hdm_results(h5_path = "hdm_models/S1/results_S1_3_70.h5", 
                    twodm_path = "hdm_models/S1/S1_mesh_computational-mesh1.2dm",
                    shp_path = "raster_files/S1_shape.shp", 
                    raster_v_path = "raster_files/S1_v_3_70.tif",
                    raster_wd_path = "raster_files/S1_wd_3_70.tif")

test_v <- raster("raster_files/S1_v_3_70.tif")
test_wd <- raster("raster_files/S1_wd_3_70.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S1_6_50 <- hdm_results(h5_path = "hdm_models/S1/results_S1_6_50.h5", 
                    twodm_path = "hdm_models/S1/S1_mesh_computational-mesh1.2dm",
                    shp_path = "raster_files/S1_shape.shp", 
                    raster_v_path = "raster_files/S1_v_6_50.tif",
                    raster_wd_path = "raster_files/S1_wd_6_50.tif")

test_v <- raster("raster_files/S1_v_6_50.tif")
test_wd <- raster("raster_files/S1_wd_6_50.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S1_8_50 <- hdm_results(h5_path = "hdm_models/S1/results_S1_8_50.h5", 
                    twodm_path = "hdm_models/S1/S1_mesh_computational-mesh1.2dm",
                    shp_path = "raster_files/S1_shape.shp", 
                    raster_v_path = "raster_files/S1_v_8_50.tif",
                    raster_wd_path = "raster_files/S1_wd_8_50.tif")

test_v <- raster("raster_files/S1_v_8_50.tif")
test_wd <- raster("raster_files/S1_wd_8_50.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S1_10_68 <- hdm_results(h5_path = "hdm_models/S1/results_S1_10_68.h5", 
                    twodm_path = "hdm_models/S1/S1_mesh_computational-mesh1.2dm",
                    shp_path = "raster_files/S1_shape.shp", 
                    raster_v_path = "raster_files/S1_v_10_68.tif",
                    raster_wd_path = "raster_files/S1_wd_10_68.tif")

test_v <- raster("raster_files/S1_v_10_68.tif")
test_wd <- raster("raster_files/S1_wd_10_68.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S1_13_00 <- hdm_results(h5_path = "hdm_models/S1/results_S1_13_00.h5", 
                    twodm_path = "hdm_models/S1/S1_mesh_computational-mesh1.2dm",
                    shp_path = "raster_files/S1_shape.shp", 
                    raster_v_path = "raster_files/S1_v_13_00.tif",
                    raster_wd_path = "raster_files/S1_wd_13_00.tif")

test_v <- raster("raster_files/S1_v_13_00.tif")
test_wd <- raster("raster_files/S1_wd_13_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S1_15_00 <- hdm_results(h5_path = "hdm_models/S1/results_S1_15_00.h5", 
                    twodm_path = "hdm_models/S1/S1_mesh_computational-mesh1.2dm",
                    shp_path = "raster_files/S1_shape.shp", 
                    raster_v_path = "raster_files/S1_v_15_00.tif",
                    raster_wd_path = "raster_files/S1_wd_15_00.tif")

test_v <- raster("raster_files/S1_v_15_00.tif")
test_wd <- raster("raster_files/S1_wd_15_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S1_18_00 <- hdm_results(h5_path = "hdm_models/S1/results_S1_18_00.h5", 
                    twodm_path = "hdm_models/S1/S1_mesh_computational-mesh1.2dm",
                    shp_path = "raster_files/S1_shape.shp", 
                    raster_v_path = "raster_files/S1_v_18_00.tif",
                    raster_wd_path = "raster_files/S1_wd_18_00.tif")

test_v <- raster("raster_files/S1_v_18_00.tif")
test_wd <- raster("raster_files/S1_wd_18_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S1_20_00 <- hdm_results(h5_path = "hdm_models/S1/results_S1_20_00.h5", 
                    twodm_path = "hdm_models/S1/S1_mesh_computational-mesh1.2dm",
                    shp_path = "raster_files/S1_shape.shp", 
                    raster_v_path = "raster_files/S1_v_20_00.tif",
                    raster_wd_path = "raster_files/S1_wd_20_00.tif")

test_v <- raster("raster_files/S1_v_20_00.tif")
test_wd <- raster("raster_files/S1_wd_20_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)
```

## Stacked Rasters
```{r}
S1_stacked_2_00 <- stack_raster(v_path = "raster_files/S1_v_2_00.tif",
                                wd_path = "raster_files/S1_wd_2_00.tif",
                                stack_path = "rasters_stacked/S1_2_00.grd")

S1_stacked_3_70 <- stack_raster(v_path = "raster_files/S1_v_3_70.tif",
                                wd_path = "raster_files/S1_wd_3_70.tif",
                                stack_path = "rasters_stacked/S1_3_70.grd")

S1_stacked_6_50 <- stack_raster(v_path = "raster_files/S1_v_6_50.tif",
                                wd_path = "raster_files/S1_wd_6_50.tif",
                                stack_path = "rasters_stacked/S1_6_50.grd")

S1_stacked_8_50 <- stack_raster(v_path = "raster_files/S1_v_8_50.tif",
                                wd_path = "raster_files/S1_wd_8_50.tif",
                                stack_path = "rasters_stacked/S1_8_50.grd")

S1_stacked_10_68 <- stack_raster(v_path = "raster_files/S1_v_10_68.tif",
                                wd_path = "raster_files/S1_wd_10_68.tif",
                                stack_path = "rasters_stacked/S1_10_68.grd")

S1_stacked_13_00 <- stack_raster(v_path = "raster_files/S1_v_13_00.tif",
                                wd_path = "raster_files/S1_wd_13_00.tif",
                                stack_path = "rasters_stacked/S1_13_00.grd")

S1_stacked_15_00 <- stack_raster(v_path = "raster_files/S1_v_15_00.tif",
                                wd_path = "raster_files/S1_wd_15_00.tif",
                                stack_path = "rasters_stacked/S1_15_00.grd")

S1_stacked_18_00 <- stack_raster(v_path = "raster_files/S1_v_18_00.tif",
                                wd_path = "raster_files/S1_wd_18_00.tif",
                                stack_path = "rasters_stacked/S1_18_00.grd")

S1_stacked_20_00 <- stack_raster(v_path = "raster_files/S1_v_20_00.tif",
                                wd_path = "raster_files/S1_wd_20_00.tif",
                                stack_path = "rasters_stacked/S1_20_00.grd")
```

# - Sitter: S2
## - Single Attribute Rasters
```{r}
par(mfrow=c(4,4))

S2_2_00 <- hdm_results(h5_path = "hdm_models/S2/results_S2_2_00.h5", 
                       twodm_path = "hdm_models/S2/computational-mesh-7-290323.2dm",
                       shp_path = "raster_files/S2_shape.shp", 
                       raster_v_path = "raster_files/S2_v_2_00.tif",
                       raster_wd_path = "raster_files/S2_wd_2_00.tif")

test_v <- raster("raster_files/S2_v_2_00.tif")
test_wd <- raster("raster_files/S2_wd_2_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S2_3_20 <- hdm_results(h5_path = "hdm_models/S2/results_S2_3_20.h5", 
                       twodm_path = "hdm_models/S2/computational-mesh-7-290323.2dm",
                       shp_path = "raster_files/S2_shape.shp", 
                       raster_v_path = "raster_files/S2_v_3_20.tif",
                       raster_wd_path = "raster_files/S2_wd_3_20.tif")

test_v <- raster("raster_files/S2_v_3_20.tif")
test_wd <- raster("raster_files/S2_wd_3_20.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S2_6_50 <- hdm_results(h5_path = "hdm_models/S2/results_S2_6_50.h5", 
                       twodm_path = "hdm_models/S2/computational-mesh-7-290323.2dm",
                       shp_path = "raster_files/S2_shape.shp", 
                       raster_v_path = "raster_files/S2_v_6_50.tif",
                       raster_wd_path = "raster_files/S2_wd_6_50.tif")

test_v <- raster("raster_files/S2_v_6_50.tif")
test_wd <- raster("raster_files/S2_wd_6_50.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S2_8_50 <- hdm_results(h5_path = "hdm_models/S2/results_S2_8_50.h5", 
                       twodm_path = "hdm_models/S2/computational-mesh-7-290323.2dm",
                       shp_path = "raster_files/S2_shape.shp", 
                       raster_v_path = "raster_files/S2_v_8_50.tif",
                       raster_wd_path = "raster_files/S2_wd_8_50.tif")

test_v <- raster("raster_files/S2_v_8_50.tif")
test_wd <- raster("raster_files/S2_wd_8_50.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S2_10_93 <- hdm_results(h5_path = "hdm_models/S2/results_S2_10_93.h5", 
                       twodm_path = "hdm_models/S2/computational-mesh-7-290323.2dm",
                       shp_path = "raster_files/S2_shape.shp", 
                       raster_v_path = "raster_files/S2_v_10_93.tif",
                       raster_wd_path = "raster_files/S2_wd_10_93.tif")

test_v <- raster("raster_files/S2_v_10_93.tif")
test_wd <- raster("raster_files/S2_wd_10_93.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S2_13_00 <- hdm_results(h5_path = "hdm_models/S2/results_S2_13_00.h5", 
                       twodm_path = "hdm_models/S2/computational-mesh-7-290323.2dm",
                       shp_path = "raster_files/S2_shape.shp", 
                       raster_v_path = "raster_files/S2_v_13_00.tif",
                       raster_wd_path = "raster_files/S2_wd_13_00.tif")

test_v <- raster("raster_files/S2_v_13_00.tif")
test_wd <- raster("raster_files/S2_wd_13_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S2_15_00 <- hdm_results(h5_path = "hdm_models/S2/results_S2_15_00.h5", 
                       twodm_path = "hdm_models/S2/computational-mesh-7-290323.2dm",
                       shp_path = "raster_files/S2_shape.shp", 
                       raster_v_path = "raster_files/S2_v_15_00.tif",
                       raster_wd_path = "raster_files/S2_wd_15_00.tif")

test_v <- raster("raster_files/S2_v_15_00.tif")
test_wd <- raster("raster_files/S2_wd_15_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S2_18_00 <- hdm_results(h5_path = "hdm_models/S2/results_S2_18_00.h5", 
                       twodm_path = "hdm_models/S2/computational-mesh-7-290323.2dm",
                       shp_path = "raster_files/S2_shape.shp", 
                       raster_v_path = "raster_files/S2_v_18_00.tif",
                       raster_wd_path = "raster_files/S2_wd_18_00.tif")

test_v <- raster("raster_files/S2_v_18_00.tif")
test_wd <- raster("raster_files/S2_wd_18_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)

S2_20_00 <- hdm_results(h5_path = "hdm_models/S2/results_S2_20_00.h5", 
                       twodm_path = "hdm_models/S2/computational-mesh-7-290323.2dm",
                       shp_path = "raster_files/S2_shape.shp", 
                       raster_v_path = "raster_files/S2_v_20_00.tif",
                       raster_wd_path = "raster_files/S2_wd_20_00.tif")

test_v <- raster("raster_files/S2_v_20_00.tif")
test_wd <- raster("raster_files/S2_wd_20_00.tif")
crs(test_v) <- "EPSG: 2056"
crs(test_wd) <- "EPSG: 2056"
plot(test_v)
plot(test_wd)
```

## - Stacked Rasters
2_00, 3_20, 6_50, 8_50, 10_93, 13_00, 15_00, 18_00, 20_00
```{r}
S2_stacked_2_00 <- stack_raster(v_path = "raster_files/S2_v_2_00.tif",
                                wd_path = "raster_files/S2_wd_2_00.tif",
                                stack_path = "rasters_stacked/S2_2_00.grd")

S2_stacked_3_20 <- stack_raster(v_path = "raster_files/S2_v_3_20.tif",
                                wd_path = "raster_files/S2_wd_3_20.tif",
                                stack_path = "rasters_stacked/S2_3_20.grd")

S2_stacked_6_50 <- stack_raster(v_path = "raster_files/S2_v_6_50.tif",
                                wd_path = "raster_files/S2_wd_6_50.tif",
                                stack_path = "rasters_stacked/S2_6_50.grd")

S2_stacked_8_50 <- stack_raster(v_path = "raster_files/S2_v_8_50.tif",
                                wd_path = "raster_files/S2_wd_8_50.tif",
                                stack_path = "rasters_stacked/S2_8_50.grd")

S2_stacked_10_93 <- stack_raster(v_path = "raster_files/S2_v_10_93.tif",
                                wd_path = "raster_files/S2_wd_10_93.tif",
                                stack_path = "rasters_stacked/S2_10_93.grd")

S2_stacked_13_00 <- stack_raster(v_path = "raster_files/S2_v_13_00.tif",
                                wd_path = "raster_files/S2_wd_13_00.tif",
                                stack_path = "rasters_stacked/S2_13_00.grd")

S2_stacked_15_00 <- stack_raster(v_path = "raster_files/S2_v_15_00.tif",
                                wd_path = "raster_files/S2_wd_15_00.tif",
                                stack_path = "rasters_stacked/S2_15_00.grd")

S2_stacked_18_00 <- stack_raster(v_path = "raster_files/S2_v_18_00.tif",
                                wd_path = "raster_files/S2_wd_18_00.tif",
                                stack_path = "rasters_stacked/S2_18_00.grd")

S2_stacked_20_00 <- stack_raster(v_path = "raster_files/S2_v_20_00.tif",
                                wd_path = "raster_files/S2_wd_20_00.tif",
                                stack_path = "rasters_stacked/S2_20_00.grd")
```

# Thur: TH4
## Single Attribute Rasters
11_45, 15_00, 18_00, 19_96, 22_50, 25_00, 27_00, 30_00, 32_93
```{r}
TH4_11_45 <- hdm_results(h5_path = "hdm_models/TH4/results_TH4_11_45.h5", 
                       twodm_path = "hdm_models/TH4/th4_uebersicht_computational-mesh4.2dm",
                       shp_path = "raster_files/TH4_shape.shp", 
                       raster_v_path = "raster_files/TH4_v_11_45.tif",
                       raster_wd_path = "raster_files/TH4_wd_11_45.tif")

TH4_15_00 <- hdm_results(h5_path = "hdm_models/TH4/results_TH4_15_00.h5", 
                       twodm_path = "hdm_models/TH4/th4_uebersicht_computational-mesh4.2dm",
                       shp_path = "raster_files/TH4_shape.shp", 
                       raster_v_path = "raster_files/TH4_v_15_00.tif",
                       raster_wd_path = "raster_files/TH4_wd_15_00.tif")

TH4_18_00 <- hdm_results(h5_path = "hdm_models/TH4/results_TH4_18_00.h5", 
                       twodm_path = "hdm_models/TH4/th4_uebersicht_computational-mesh4.2dm",
                       shp_path = "raster_files/TH4_shape.shp", 
                       raster_v_path = "raster_files/TH4_v_18_00.tif",
                       raster_wd_path = "raster_files/TH4_wd_18_00.tif")

TH4_19_96 <- hdm_results(h5_path = "hdm_models/TH4/results_TH4_19_96.h5", 
                       twodm_path = "hdm_models/TH4/th4_uebersicht_computational-mesh4.2dm",
                       shp_path = "raster_files/TH4_shape.shp", 
                       raster_v_path = "raster_files/TH4_v_19_96.tif",
                       raster_wd_path = "raster_files/TH4_wd_19_96.tif")

TH4_22_50 <- hdm_results(h5_path = "hdm_models/TH4/results_TH4_22_50.h5", 
                       twodm_path = "hdm_models/TH4/th4_uebersicht_computational-mesh4.2dm",
                       shp_path = "raster_files/TH4_shape.shp", 
                       raster_v_path = "raster_files/TH4_v_22_50.tif",
                       raster_wd_path = "raster_files/TH4_wd_22_50.tif")

TH4_25_00 <- hdm_results(h5_path = "hdm_models/TH4/results_TH4_25_00.h5", 
                       twodm_path = "hdm_models/TH4/th4_uebersicht_computational-mesh4.2dm",
                       shp_path = "raster_files/TH4_shape.shp", 
                       raster_v_path = "raster_files/TH4_v_25_00.tif",
                       raster_wd_path = "raster_files/TH4_wd_25_00.tif")

TH4_27_00 <- hdm_results(h5_path = "hdm_models/TH4/results_TH4_27_00.h5", 
                       twodm_path = "hdm_models/TH4/th4_uebersicht_computational-mesh4.2dm",
                       shp_path = "raster_files/TH4_shape.shp", 
                       raster_v_path = "raster_files/TH4_v_27_00.tif",
                       raster_wd_path = "raster_files/TH4_wd_27_00.tif")

TH4_30_00 <- hdm_results(h5_path = "hdm_models/TH4/results_TH4_30_00.h5", 
                       twodm_path = "hdm_models/TH4/th4_uebersicht_computational-mesh4.2dm",
                       shp_path = "raster_files/TH4_shape.shp", 
                       raster_v_path = "raster_files/TH4_v_30_00.tif",
                       raster_wd_path = "raster_files/TH4_wd_30_00.tif")

TH4_32_93 <- hdm_results(h5_path = "hdm_models/TH4/results_TH4_32_93.h5", 
                       twodm_path = "hdm_models/TH4/th4_uebersicht_computational-mesh4.2dm",
                       shp_path = "raster_files/TH4_shape.shp", 
                       raster_v_path = "raster_files/TH4_v_32_93.tif",
                       raster_wd_path = "raster_files/TH4_wd_32_93.tif")
```

## Stacked Rasters
```{r}
TH4_stacked_11_45 <- stack_raster(v_path = "raster_files/TH4_v_11_45.tif",
                                wd_path = "raster_files/TH4_wd_11_45.tif",
                                stack_path = "rasters_stacked/TH4_11_45.grd")

TH4_stacked_15_00 <- stack_raster(v_path = "raster_files/TH4_v_15_00.tif",
                                wd_path = "raster_files/TH4_wd_15_00.tif",
                                stack_path = "rasters_stacked/TH4_15_00.grd")

TH4_stacked_18_00 <- stack_raster(v_path = "raster_files/TH4_v_18_00.tif",
                                wd_path = "raster_files/TH4_wd_18_00.tif",
                                stack_path = "rasters_stacked/TH4_18_00.grd")

TH4_stacked_19_96 <- stack_raster(v_path = "raster_files/TH4_v_19_96.tif",
                                wd_path = "raster_files/TH4_wd_19_96.tif",
                                stack_path = "rasters_stacked/TH4_19_96.grd")

TH4_stacked_22_50 <- stack_raster(v_path = "raster_files/TH4_v_22_50.tif",
                                wd_path = "raster_files/TH4_wd_22_50.tif",
                                stack_path = "rasters_stacked/TH4_22_50.grd")

TH4_stacked_25_00 <- stack_raster(v_path = "raster_files/TH4_v_25_00.tif",
                                wd_path = "raster_files/TH4_wd_25_00.tif",
                                stack_path = "rasters_stacked/TH4_25_00.grd")

TH4_stacked_27_00 <- stack_raster(v_path = "raster_files/TH4_v_27_00.tif",
                                wd_path = "raster_files/TH4_wd_27_00.tif",
                                stack_path = "rasters_stacked/TH4_27_00.grd")

TH4_stacked_30_00 <- stack_raster(v_path = "raster_files/TH4_v_30_00.tif",
                                wd_path = "raster_files/TH4_wd_30_00.tif",
                                stack_path = "rasters_stacked/TH4_30_00.grd")

TH4_stacked_32_93 <- stack_raster(v_path = "raster_files/TH4_v_32_93.tif",
                                wd_path = "raster_files/TH4_wd_32_93.tif",
                                stack_path = "rasters_stacked/TH4_32_93.grd")
```

# Vorderrhein: VR3
## Single Attribute Rasters
2_90, 6_00, 9_00, 12_00, 15_00, 18_80, 22_00, 25_00, 28_00, 31_00, 34_00, 37_00, 40_10, 43_00, 46_00, 48_00, 50_00, 52_90
```{r}
VR3_2_90 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_2_90.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_2_90.tif",
                       raster_wd_path = "raster_files/VR3_wd_2_90.tif")

VR3_6_00 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_6_00.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_6_00.tif",
                       raster_wd_path = "raster_files/VR3_wd_6_00.tif")

VR3_9_00 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_9_00.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_9_00.tif",
                       raster_wd_path = "raster_files/VR3_wd_9_00.tif")

VR3_12_00 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_12_00.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_12_00.tif",
                       raster_wd_path = "raster_files/VR3_wd_12_00.tif")

VR3_15_00 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_15_00.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_15_00.tif",
                       raster_wd_path = "raster_files/VR3_wd_15_00.tif")

VR3_18_80 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_18_80.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_18_80.tif",
                       raster_wd_path = "raster_files/VR3_wd_18_80.tif")

VR3_22_00 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_22_00.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_22_00.tif",
                       raster_wd_path = "raster_files/VR3_wd_22_00.tif")

VR3_25_00 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_25_00.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_25_00.tif",
                       raster_wd_path = "raster_files/VR3_wd_25_00.tif")

VR3_28_00 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_28_00.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_28_00.tif",
                       raster_wd_path = "raster_files/VR3_wd_28_00.tif")

VR3_31_00 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_31_00.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_31_00.tif",
                       raster_wd_path = "raster_files/VR3_wd_31_00.tif")

VR3_34_00 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_34_00.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_34_00.tif",
                       raster_wd_path = "raster_files/VR3_wd_34_00.tif")

VR3_37_00 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_37_00.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_37_00.tif",
                       raster_wd_path = "raster_files/VR3_wd_37_00.tif")

VR3_40_10 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_40_10.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_40_10.tif",
                       raster_wd_path = "raster_files/VR3_wd_40_10.tif")

VR3_43_00 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_43_00.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_43_00.tif",
                       raster_wd_path = "raster_files/VR3_wd_43_00.tif")

VR3_46_00 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_46_00.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_46_00.tif",
                       raster_wd_path = "raster_files/VR3_wd_46_00.tif")

VR3_48_00 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_48_00.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_48_00.tif",
                       raster_wd_path = "raster_files/VR3_wd_48_00.tif")

VR3_50_00 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_50_00.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_50_00.tif",
                       raster_wd_path = "raster_files/VR3_wd_50_00.tif")

VR3_52_90 <- hdm_results(h5_path = "hdm_models/VR3/results_VR3_52_90.h5", 
                       twodm_path = "hdm_models/VR3/VR_computational-mesh_3.2dm",
                       shp_path = "raster_files/VR3_shape.shp", 
                       raster_v_path = "raster_files/VR3_v_52_90.tif",
                       raster_wd_path = "raster_files/VR3_wd_52_90.tif")
```

## Stacked Rasters
```{r}
VR3_stacked_2_90 <- stack_raster(v_path = "raster_files/VR3_v_2_90.tif",
                                wd_path = "raster_files/VR3_wd_2_90.tif",
                                stack_path = "rasters_stacked/VR3_2_90.grd")

VR3_stacked_6_00 <- stack_raster(v_path = "raster_files/VR3_v_6_00.tif",
                                wd_path = "raster_files/VR3_wd_6_00.tif",
                                stack_path = "rasters_stacked/VR3_6_00.grd")

VR3_stacked_9_00 <- stack_raster(v_path = "raster_files/VR3_v_9_00.tif",
                                wd_path = "raster_files/VR3_wd_9_00.tif",
                                stack_path = "rasters_stacked/VR3_9_00.grd")

VR3_stacked_12_00 <- stack_raster(v_path = "raster_files/VR3_v_12_00.tif",
                                wd_path = "raster_files/VR3_wd_12_00.tif",
                                stack_path = "rasters_stacked/VR3_12_00.grd")

VR3_stacked_15_00 <- stack_raster(v_path = "raster_files/VR3_v_15_00.tif",
                                wd_path = "raster_files/VR3_wd_15_00.tif",
                                stack_path = "rasters_stacked/VR3_15_00.grd")

VR3_stacked_18_80 <- stack_raster(v_path = "raster_files/VR3_v_18_80.tif",
                                wd_path = "raster_files/VR3_wd_18_80.tif",
                                stack_path = "rasters_stacked/VR3_18_80.grd")

VR3_stacked_22_00 <- stack_raster(v_path = "raster_files/VR3_v_22_00.tif",
                                wd_path = "raster_files/VR3_wd_22_00.tif",
                                stack_path = "rasters_stacked/VR3_22_00.grd")

VR3_stacked_25_00 <- stack_raster(v_path = "raster_files/VR3_v_25_00.tif",
                                wd_path = "raster_files/VR3_wd_25_00.tif",
                                stack_path = "rasters_stacked/VR3_25_00.grd")

VR3_stacked_28_00 <- stack_raster(v_path = "raster_files/VR3_v_28_00.tif",
                                wd_path = "raster_files/VR3_wd_28_00.tif",
                                stack_path = "rasters_stacked/VR3_28_00.grd")

VR3_stacked_31_00 <- stack_raster(v_path = "raster_files/VR3_v_31_00.tif",
                                wd_path = "raster_files/VR3_wd_31_00.tif",
                                stack_path = "rasters_stacked/VR3_31_00.grd")

VR3_stacked_34_00 <- stack_raster(v_path = "raster_files/VR3_v_34_00.tif",
                                wd_path = "raster_files/VR3_wd_34_00.tif",
                                stack_path = "rasters_stacked/VR3_34_00.grd")

VR3_stacked_37_00 <- stack_raster(v_path = "raster_files/VR3_v_37_00.tif",
                                wd_path = "raster_files/VR3_wd_37_00.tif",
                                stack_path = "rasters_stacked/VR3_37_00.grd")

VR3_stacked_40_10 <- stack_raster(v_path = "raster_files/VR3_v_40_10.tif",
                                wd_path = "raster_files/VR3_wd_40_10.tif",
                                stack_path = "rasters_stacked/VR3_40_10.grd")

VR3_stacked_43_00 <- stack_raster(v_path = "raster_files/VR3_v_43_00.tif",
                                wd_path = "raster_files/VR3_wd_43_00.tif",
                                stack_path = "rasters_stacked/VR3_43_00.grd")

VR3_stacked_46_00 <- stack_raster(v_path = "raster_files/VR3_v_46_00.tif",
                                wd_path = "raster_files/VR3_wd_46_00.tif",
                                stack_path = "rasters_stacked/VR3_46_00.grd")

VR3_stacked_48_00 <- stack_raster(v_path = "raster_files/VR3_v_48_00.tif",
                                wd_path = "raster_files/VR3_wd_48_00.tif",
                                stack_path = "rasters_stacked/VR3_48_00.grd")

VR3_stacked_50_00 <- stack_raster(v_path = "raster_files/VR3_v_50_00.tif",
                                wd_path = "raster_files/VR3_wd_50_00.tif",
                                stack_path = "rasters_stacked/VR3_50_00.grd")

VR3_stacked_52_90 <- stack_raster(v_path = "raster_files/VR3_v_52_90.tif",
                                wd_path = "raster_files/VR3_wd_52_90.tif",
                                stack_path = "rasters_stacked/VR3_52_90.grd")
```

# Extract/Rekonstruct Discharges
Idee: stacked raster fr v und wd erstellen pro section, dann extract 
## Glenner: GL1
```{r}
# read stacked rasters (wd + v per discharge)
GL1_3_28 <- raster("raster_files/GL1_wd_3_28.tif")
GL1_6_00 <- raster("rasters_stacked/GL1_6_00.grd")
GL1_9_00 <- raster("rasters_stacked/GL1_9_00.grd")
GL1_31_76 <- raster("rasters_stacked/GL1_31_76.grd")
GL1_31_76 <- raster("raster_files/GL1_wd_31_76.tif")

plot(raster("raster_files/L2_wd_2_40.tif"))
plot(raster("raster_files/L2_wd_18_90.tif"))

# stack rasters into one stack
GL1_stacked <- stack(GL1_3_28, GL1_6_00, GL1_9_00, GL1_31_76)

plot(GL1_stacked)
plot(GL1_3_28)
plot(GL1_31_76)
```