---
title: "Reconstruct Discharges of Sampling Days"
format: html
---

# Load packages
```{r}
# clear R memory 
rm(list = ls())

# load packages 
pkgCheck <- function(x){ 
  if (!require(x,character.only = TRUE)){
    install.packages(x,dependencies=TRUE)
    if(!require(x,character.only = TRUE)) {
      stop()
    }
  }
}

pkgCheck("raster")
pkgCheck("spsurvey")
pkgCheck("terra")
pkgCheck("ggplot2")
pkgCheck("tibble")
pkgCheck("readr")
pkgCheck("dplyr")
pkgCheck("tidyr")
pkgCheck("scales")
pkgCheck("hdf5r")
pkgCheck("sp")
pkgCheck("sf")
pkgCheck("spatstat.geom")
pkgCheck("spatstat.explore")
pkgCheck("gstat")
pkgCheck("purrr")
pkgCheck("rgdal")

# load self-written functions 
source("mth_functions.R")

# set working directory 
setwd("Pre_Processing")
```

Q_study_site_MZB = Q_pegel_MZB * Q_model_site / Q_pegel_model

mit einzugsgebiet einbezogen:
Q_study_site_MZB = Q_studysite_area / Q_pegel_area * Q_pegel_MZB

*Q_study_site_MZB:* gesuchter Abfluss am Tag und Uhrzeit des Samplings in der Sektion (=Study site)
*Q_pegel_MZB:* am nächstgelegenen Pegel gemessener Abfluss am Tag und Uhrzeit des Samplings (diese Info müsste in der Abiotik tabelle von Diego drin sein)
*Q_model_site:* im study site gemessenen Abfluss am Tag und Uhrzeit der Feldaufnahmen für das Modell (findest du in der Tabelle, die ich dir am 3.8. geschickt habe)
*Q_pegel_model:* am nächstgelegenen Pegel gemessener Abfluss am Tag und Uhrzeit der Feldaufnahmen für das Modell. 

# Reconstruct 
## Q_model_site
Als Abflusswert für GL1 kannst du die 11 m3/s nehmen, die wir auf Gl2 gemessen haben, da es zwischen Gl1 und Gl2 keine grosse Zuflüsse vorhanden sind.
```{r}
# Discharge measured in the study site on the day and time of the field recordings for the hydrodynamic model 

Q_model_GL1 <- 11.0 
Q_model_GL2 <- 11.0
Q_model_L2 <- 7.0
Q_model_M1 <- 0.6
Q_model_S1 <- 3.7
Q_model_S2 <- 3.2
Q_model_TH4 <- 25.0
Q_model_VR3 <- 18.8
```

## Q_MI_site
```{r}
# Extract Q of MI sampling days for all sections (from abiotic data)
# Load MI Data
mzb_data <- read_delim("abiotic_mi_sampling/Abiotic_MI_Lab.csv")

# select relevant columns 
data <- mzb_data %>%
  mutate(mean_Q = rowMeans(dplyr::select(., Discharge_m3_s_before,
                                  Discharge_m3_s_during,
                                  Discharge_m3_s_after))) %>%
  dplyr::select(Reach_Untersuchungsstelle, Discharge_m3_s_before,
                Discharge_m3_s_after,
                Discharge_m3_s_during, mean_Q)


# select only single river sections and calculate mean Q per river section 
# GL1
Q_MI_GL1 <- data |>
  subset(Reach_Untersuchungsstelle == "GL1") |>
  dplyr::select(Reach_Untersuchungsstelle, mean_Q) |>
  summarise(Q_MI_GL1 = mean(mean_Q)) 

# GL2
Q_MI_GL2 <- data |>
  subset(Reach_Untersuchungsstelle == "GL2") |>
  dplyr::select(Reach_Untersuchungsstelle, mean_Q) |>
  summarise(Q_MI_GL2 =mean(mean_Q))

# L2
Q_MI_L2 <- data |>
  subset(Reach_Untersuchungsstelle == "L2") |>
  dplyr::select(Reach_Untersuchungsstelle, mean_Q) |>
  summarise(Q_MI_L2 = mean(mean_Q))

# M1
Q_MI_M1 <- data |>
  subset(Reach_Untersuchungsstelle == "M1") |>
  dplyr::select(Reach_Untersuchungsstelle, mean_Q) |>
  summarise(Q_MI_M1 = mean(mean_Q))

# S1
Q_MI_S1 <- data |>
  subset(Reach_Untersuchungsstelle == "S1") |>
  dplyr::select(Reach_Untersuchungsstelle, mean_Q) |>
  summarise(Q_MI_S1 = mean(mean_Q))

# S2
Q_MI_S2 <- data |>
  subset(Reach_Untersuchungsstelle == "S2") |>
  dplyr::select(Reach_Untersuchungsstelle, mean_Q) |>
  summarise(Q_MI_S2 = mean(mean_Q))

# TH4
Q_MI_TH4 <- data |>
  subset(Reach_Untersuchungsstelle == "TH4") |>
  dplyr::select(Reach_Untersuchungsstelle, mean_Q) |>
  summarise(Q_MI_TH4 = mean(mean_Q))

# VR3
Q_MI_VR3 <- data |>
  subset(Reach_Untersuchungsstelle == "VR3") |>
  dplyr::select(Reach_Untersuchungsstelle, mean_Q) |>
  summarise(Q_MI_VR3 = mean(mean_Q))
```

## Q_pegel_site
```{r}
# Assign discharge of nearest gauging station at the time of MI sampling
Q_pegel_GL1 <- "x"
Q_pegel_GL2 <- "x"
Q_pegel_L2 <- "x"
Q_pegel_M1 <- "x"
Q_pegel_S1 <- "x"
Q_pegel_S2 <- "x"
Q_pegel_TH4 <- "x"
Q_pegel_VR3 <- "x"
```

## ! Calculate Q 
```{r}
# reconstuct discharges using the formula from the beginning 
Q_sampling_GL1 <- Q_MI_GL1 * Q_model_GL1 / Q_pegel_GL1
Q_sampling_GL2 <- Q_MI_GL2 * Q_model_GL2 / Q_pegel_GL2
Q_sampling_L2 <- Q_MI_L2 * Q_model_L2 / Q_pegel_L2
Q_sampling_M1 <- Q_MI_M1 * Q_model_M1 / Q_pegel_M1
Q_sampling_S1 <- Q_MI_S1 * Q_model_S1 / Q_pegel_S1
Q_sampling_S2 <- Q_MI_S2 * Q_model_S2 / Q_pegel_S2
Q_sampling_TH4 <- Q_MI_TH4 * Q_model_TH4 / Q_pegel_TH4
Q_sampling_VR3 <- Q_MI_VR3 * Q_model_VR3 / Q_pegel_VR3
```

## Save results 
```{r}
# Put all results into a dataframe 
results <- data.frame(Q_model = c(Q_model_GL1, Q_model_GL2, Q_model_L2, Q_model_M1,
                                  Q_model_S1,Q_model_S2, Q_model_TH4, Q_model_VR3), 
                      Q_MI = c(Q_MI_GL1$Q_MI_GL1, Q_MI_GL2$Q_MI_GL2, Q_MI_L2$Q_MI_L2,
                               Q_MI_M1$Q_MI_M1, Q_MI_S1$Q_MI_S1, Q_MI_S2$Q_MI_S2,
                               Q_MI_TH4$Q_MI_TH4, Q_MI_VR3$Q_MI_VR3), 
                      Q_pegel = c(Q_pegel_GL1, Q_pegel_GL2, Q_pegel_L2, Q_pegel_M1,
                                  Q_pegel_S1,Q_pegel_S2, Q_pegel_TH4, Q_pegel_VR3), 
                      Q_reconstructed = c(Q_sampling_GL1, Q_sampling_GL2, Q_sampling_L2,
                                          Q_sampling_M1, Q_sampling_S1, Q_sampling_S2,
                                          Q_sampling_TH4, Q_sampling_VR3),
                      section = c("GL1", "GL2", "L2", "M1", "S1", "S2", "TH4", "VR3"))


# Save results as .csv - file 
write.csv(results, "reconstructed_discharges.csv", row.names = FALSE)
```

# Regression Analysis Prep
## Load Rasters
```{r}
# read rasters containing wd and velocity 
GL1_samp <- stack("Pre_Processing/rasters_stacked/GL1_3_28.grd")
GL2_samp <- stack("Pre_Processing/rasters_stacked/GL2_3_21.grd")
L2_samp <- stack("Pre_Processing/rasters_stacked/L2_2_40.grd")
M1_samp <- stack("Pre_Processing/rasters_stacked/M1_0_47.grd")
S1_samp <- stack("Pre_Processing/rasters_stacked/S1_2_00.grd")
S2_samp <- stack("Pre_Processing/rasters_stacked/S2_2_00.grd")
TH4_samp <- stack("Pre_Processing/rasters_stacked/TH4_11_45.grd")
VR3_samp <- stack("Pre_Processing/rasters_stacked/VR3_2_90.grd")

# rename raster 
names(GL1_samp) <- c("velocity", "wd_cm")  # Replace with your desired new names
names(GL2_samp) <- c("velocity", "wd_cm")  # Replace with your desired new names
names(L2_samp) <- c("velocity", "wd_cm")  # Replace with your desired new names
names(M1_samp) <- c("velocity", "wd_cm")  # Replace with your desired new names
names(S1_samp) <- c("velocity", "wd_cm")  # Replace with your desired new names
names(S2_samp) <- c("velocity", "wd_cm")  # Replace with your desired new names
names(TH4_samp) <- c("velocity", "wd_cm")  # Replace with your desired new names
names(VR3_samp) <- c("velocity", "wd_cm")  # Replace with your desired new names

# assign coordinate system 
crs(GL1_samp) <- "EPSG: 2056"
crs(GL2_samp) <- "EPSG: 2056"
crs(L2_samp) <- "EPSG: 2056"
crs(M1_samp) <- "EPSG: 2056"
crs(S1_samp) <- "EPSG: 2056"
crs(S2_samp) <- "EPSG: 2056"
crs(TH4_samp) <- "EPSG: 2056"
crs(VR3_samp) <- "EPSG: 2056"
```

## Load Data
```{r}
# load data 
data_wd <- read_delim("Pre_Processing/abiotic_mi_sampling/lab_ml_wd_v.csv") |>
  mutate(Reach_Untersuchungsstelle = as.factor(Reach_Untersuchungsstelle), # convert character variables into categorical variables (factors with levels) for ML algorithm 
         velocity = velocity/100,  # convert cm/s in to m/s (to have the same units as the hdms)
         wd_cm = wd_cm/100) # convert cm in to m (to have the same units as the hdms)

# read all raster results (one time flow velocity classes and one time for habitat suitability)
# prep extraction data 
## GL1
coord_GL1 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "GL1") |>
  dplyr::select(x, y) 

GL1 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "GL1")

## GL2
coord_GL2 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "GL2") |>
  dplyr::select(x, y) 

GL2 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "GL2")

## L2
coord_L2 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "L2") |>
  dplyr::select(x, y) 

L2 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "L2")

## M1
coord_M1 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "M1") |>
  dplyr::select(x, y) 

M1 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "M1")

## S1
coord_S1 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "S1") |>
  dplyr::select(x, y) 

S1 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "S1")

## S2
coord_S2 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "S2") |>
  dplyr::select(x, y) 

S2 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "S2")

## TH4
coord_TH4 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "TH4") |>
  dplyr::select(x, y) 

TH4 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "TH4")

## VR3
coord_VR3 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "VR3") |>
  dplyr::select(x, y) 

VR3 <- data_wd |>
  subset(Reach_Untersuchungsstelle == "VR3")
```

### Extract Results
```{r}
# extract raster information for regression analysis later
# GL1 
regr_data_GL1_wd <- extract(GL1_samp, coord_GL1) 

# GL2
regr_data_GL2_wd <- extract(GL2_samp, coord_GL2) 

# L2
regr_data_L2_wd <- extract(L2_samp, coord_L2) 

# M1
regr_data_M1_wd <- extract(M1_samp, coord_M1) 

# S1
regr_data_S1_wd <- extract(S1_samp, coord_S1) 

# S2
regr_data_S2_wd <- extract(S2_samp, coord_S2) 

# TH4
regr_data_TH4_wd <- extract(TH4_samp, coord_TH4) 

# VR3
regr_data_VR3_wd <- extract(VR3_samp, coord_VR3) 
```

### Combine Results
```{r}
# combine all results into dataframe
# GL1
data_GL1 <- cbind(regr_rf_data_GL1_wd_k, regr_rf_data_GL1_wd_s, regr_rf_data_GL1_wd_a, regr_rf_data_GL1_v_k, regr_rf_data_GL1_v_s, regr_rf_data_GL1_v_a, regr_brt_data_GL1_wd_k, regr_brt_data_GL1_wd_s, regr_brt_data_GL1_wd_a, regr_brt_data_GL1_v_k, regr_brt_data_GL1_v_s, regr_brt_data_GL1_v_a, GL1) |>
  rename(rf_pred_k_index_2 = regr_rf_data_GL1_wd_k,
         rf_pred_shannon_2 = regr_rf_data_GL1_wd_s,
         rf_pred_abundance_2 = regr_rf_data_GL1_wd_a,
         rf_pred_k_index_v = regr_rf_data_GL1_v_k,
         rf_pred_shannon_v = regr_rf_data_GL1_v_s,
         rf_pred_abundance_v = regr_rf_data_GL1_v_a,
         brt_pred_k_index_2 = regr_brt_data_GL1_wd_k,
         brt_pred_shannon_2 = regr_brt_data_GL1_wd_s,
         brt_pred_abundance_2 = regr_brt_data_GL1_wd_a,
         brt_pred_k_index_v = regr_brt_data_GL1_v_k,
         brt_pred_shannon_v = regr_brt_data_GL1_v_s,
         brt_pred_abundance_v = regr_brt_data_GL1_v_a,
         obs_k_index = k_index,
         obs_shannon = shannon,
         obs_abundance = abundance)
```

### Results from Extraction 
```{r}
# bind results together 
# data_TH4 fehlt noch
regr_analysis <- rbind(data_GL1, data_GL2, data_L2, data_M1, data_S1, data_S2, data_TH4, data_VR3)

# export to .csv file
write.csv(regr_analysis, "Stat_Analysis/ml_regr_analysis.csv", row.names = FALSE)
```


